Notes on two photon scattering of the molecular state

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] tweak format, add v=0 off resonance PA rate measurement, add summary

\begin{enumerate}
\item Line width and decay time measurement of Raman process near $v=0$ ($1038 \mathrm{nm}$)\\
  The result is consistent with a $300 \mathrm{MHz}$ to $600 \mathrm{MHz}$
  excited state line width.\\
  We did not make a power dependency measurement.\\
  We measured carefully at multiple red detunings, which all shows similar results.\\
  We measured one point not as carefully for blue detuning
  ($18 \mathrm{GHz}$ or $10 \mathrm{GHz}$ detuned depending on the excited state $J$)
  which shows similar result as the corresponding red detuning.
\item Excited state line width for $v=0$.\\
  The line width is narrow ($\leqslant 50 \mathrm{MHz}$)
  when the tweezer is near $976 \mathrm{nm}$ but is wide ($\geqslant 500 \textrm{MHz}$)
  when the tweezer is near $1038 \mathrm{nm}$ red detuned from the $v=0$ resonance
  by a few hundred GHz.\\
  We did not make a power dependency measurement.
\item Line width of a ``mysterious'' line\\
  Tweezer $100 \mathrm{GHz}$ red detuned.\\
  Line width $\approx 100 \mathrm{MHz}$
  (determined to be narrow at the time but could have some broadening)\\
  We did not make a power dependency measurement.
\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
  in $307366 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The dependency of the loss rate to tweezer power is consistent with the prediction of
  a two photo process from the tweezer. In another word, it is consistent with
  a excited state broadened proportional to the tweezer power.
\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
  in $306638 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The power dependency may be consistent with a single photon process.
\item $v=12$ line width.\\
  Narrow ($25 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (blue detuned $\approx 900\mathrm{GHz}$). (No tweezer power dependency taken.)\\
  Narrow ($20 \mathrm{MHz}$) for tweezer at $306612 \mathrm{GHz}$
  (blue detuned $\approx 130\mathrm{GHz}$). (No tweezer power dependency taken.)
  We have also indirectly observed a Raman coupling to a deeper molecular bound state
  between the tweezer and the PA probe beam.\\
  Broad ($250 \mathrm{MHz}$) for tweezer at $306344.5 \mathrm{GHz}$
  (red detuned $\approx 150\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item $v=14$ line width.\\
  Broad ($200 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (red detuned $\approx 1900\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item Raman blue detuned from $v=12$.\\
  Tweezer at around $306614 \mathrm{GHz}$.\\
  No Rabi flopping observed.
\end{enumerate}

@@

      \begin{scope}[shift={(2.6, 0)}]
        % \draw[dashed] (-0.05, 0) -- (1.5, 0);
        % \draw[dashed] (-0.05, 2.15) -- (1.5, 2.15);
        % \draw[dashed] (-0.05, 2.45) -- (1.5, 2.45);

        \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
        \draw[line width=1] (1.5, 2.15) -- (2, 2.15) node[right] {$|-\rangle$};
        \draw[line width=1] (1.5, 2.45) -- (2, 2.45) node[right] {$|+\rangle$};
        \draw[line width=1] (0.2, 0) -- node[below] {$|g'\rangle$} (0.7, 0);
        \draw[<->, line width=1, blue] (2, 0) -- node[right]
        {$\frac{D_1}{\sqrt2}$} (2, 2.15);
        \draw[<->, line width=1, blue] (1.9, 0) -- node[above left]
        {$\frac{D_1}{\sqrt2}$} (1.9, 2.45);
        \draw[<->, line width=1, red] (0.2, 0) -- node[left=0.1]
        {$\frac{D'}{\sqrt2}$} (1.5, 2.45);
        \draw[<->, line width=1, red] (0.43, 0) -- (1.6, 2.15);
        \node[red, below right] at (0.9, 1.075) {$\frac{-D'}{\sqrt2}$};

@@

>>>>

\begin{enumerate}
\item Line width and decay time measurement of Raman process near $v=0$ ($1038 \mathrm{nm}$)\\
  The result is consistent with a $300 \mathrm{MHz}$ to $600 \mathrm{MHz}$
  excited state line width.\\
  We did not make a power dependency measurement.\\
  We measured carefully at multiple red detunings, which all shows similar results.\\
  We measured one point not as carefully for blue detuning
  ($18 \mathrm{GHz}$ or $10 \mathrm{GHz}$ detuned depending on the excited state $J$)
  which shows similar result as the corresponding red detuning.
\item Off resonance PA rate (lifetime) in $|F^{\mathrm{Cs}}\!=\!4, m_{F}^{\mathrm{Cs}}\!=\!4; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$
  near $v=0$ PA line.\\
  The result is consistent with the Raman line width and decay time measurements above
  which gives a wide excited state line width.
\item Excited state line width for $v=0$.\\
  The line width is narrow ($\leqslant 50 \mathrm{MHz}$)
  when the tweezer is near $976 \mathrm{nm}$ but is wide ($\geqslant 500 \textrm{MHz}$)
  when the tweezer is near $1038 \mathrm{nm}$ red detuned from the $v=0$ resonance
  by a few hundred GHz.\\
  We did not make a power dependency measurement.
\item Line width of a ``mysterious'' line\\
  Tweezer $100 \mathrm{GHz}$ red detuned.\\
  Line width $\approx 100 \mathrm{MHz}$
  (determined to be narrow at the time but could have some broadening)\\
  We did not make a power dependency measurement.
\item $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ lifetime
  in $307366 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The dependency of the loss rate to tweezer power is consistent with the prediction of
  a two photo process from the tweezer. In another word, it is consistent with
  a excited state broadened proportional to the tweezer power.
\item $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ lifetime
  in $306638 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The power dependency may be consistent with a single photon process.
\item $v=12$ line width.\\
  Narrow ($25 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (blue detuned $\approx 900\mathrm{GHz}$). (No tweezer power dependency taken.)\\
  Narrow ($20 \mathrm{MHz}$) for tweezer at $306612 \mathrm{GHz}$
  (blue detuned $\approx 130\mathrm{GHz}$). (No tweezer power dependency taken.)
  We have also indirectly observed a Raman coupling to a deeper molecular bound state
  between the tweezer and the PA probe beam.\\
  Broad ($250 \mathrm{MHz}$) for tweezer at $306344.5 \mathrm{GHz}$
  (red detuned $\approx 150\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item $v=14$ line width.\\
  Broad ($200 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (red detuned $\approx 1900\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item Raman blue detuned from $v=12$.\\
  Tweezer at around $306614 \mathrm{GHz}$.\\
  No Rabi flopping observed.
\end{enumerate}

@@

      \begin{scope}[shift={(2.6, 0)}]
        \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
        \draw[line width=1] (1.5, 2.15) -- (2, 2.15) node[right] {$|-\rangle$};
        \draw[line width=1] (1.5, 2.45) -- (2, 2.45) node[right] {$|+\rangle$};
        \draw[line width=1] (0.2, 0) -- node[below] {$|g'\rangle$} (0.7, 0);
        \draw[<->, line width=1, blue] (2, 0) -- node[right]
        {$\frac{D_1}{\sqrt2}$} (2, 2.15);
        \draw[<->, line width=1, blue] (1.9, 0) -- node[above left]
        {$\frac{D_1}{\sqrt2}$} (1.9, 2.45);
        \draw[<->, line width=1, red] (0.2, 0) -- node[left=0.1]
        {$\frac{D'}{\sqrt2}$} (1.5, 2.45);
        \draw[<->, line width=1, red] (0.43, 0) -- (1.6, 2.15);
        \node[red, below right] at (0.9, 1.075) {$\frac{-D'}{\sqrt2}$};

@@

\subsubsection{Summary for two photon coupling down}

In the particular case (two photon excite to a single state) we calculated,
the naive calculation using coupled excited state (i.e. direct result from PA measurement)
gives the wrong result because of the interference from different scattering channels.
More generally, to avoid this problem one need to realize,
\begin{enumerate}
\item The scattering is never a one photon process, one need to calculate the rate
  after considering all photon involved.
\item It is OK to couple some intermediate states first and use a dressed state picture
  to eliminate the number of photon/coupling/intermediate states involved. However,
  the coupled result may not be a single state and the scattering from the resulting
  states may not follow a simple $\Delta^{-2}$ rule.
\end{enumerate}
